A fast unified model for parsing and sentence understanding

### 2016-03-15 writing/hard_stack_paper/paper.tex
Edit results section

\paragraph{Results} Table~\ref{tab:results} shows our results. Our primary evaluation metric for all models is three-way classification accuracy on the SNLI test set. For the full SPINN model, we also report a measure of the agreement of its generated parses with the Stanford Parser's parses of the same data, expressed in terms of the model's accuracy in making two-way transition decisions. In addition, we report the number of trained parameters in each model as well as training set accuracy.

We find that the bare SPINN-NP-NT model performs relatively poorly, but that the SPINN-NP with the added tracking LSTM reaches state-of-the-art accuracy among sentence encoding based models, indicating that our tree-sequence hybrid approach succeeds in combining the strengths of both approaches to encoding. The fully independent SPINN model with its relatively weak internal parser performs more poorly, but nonetheless exceeds the performance of the LSTM baseline. None of our models reached the performance of the strongest attention-based models, which were explicitly engineered for the sentence pair-based structure of the SNLI task.

@@

\begin{figure}
\resizebox{\linewidth}{!}{
\begin{tikzpicture}
\begin{axis}[xmin=0, ymin=0, xlabel=Batch size, ylabel=Feedforward time (sec),
			 xtick={0,256,512,1024,2048}, legend style={at={(1, 1)},anchor=north east}]
  \addplot table [x={Batch size}, y=CPU, col sep=tab] {runtime.csv};
  \addlegendentry{CPU \cite{irsoy2014deep}}
  \addplot table [x={Batch size}, y=GPU, col sep=tab] {runtime.csv};
  \addlegendentry{Thin-stack GPU}
\end{axis}
\end{tikzpicture}
}
\caption{Runtime performance results with the thin-stack GPU algorithm for tree-structured neural networks. \todo{[JG] Add some comments}}
\end{figure}

>>>>

\paragraph{Results} Table~\ref{tab:results} shows our results. Our primary evaluation metric for all models is three-way classification accuracy on the SNLI test set. The full SPINN model also generates parsing predictions, and we report a measure of agreement between this model's predictions and the Stanford Parser's predictions on the same data (calculated as classification accuracy over \shift~and \reduce~operations). We also report the number of trained parameters in each model and training set accuracy.

We find that the bare SPINN-NP-NT model performs relatively poorly, but that the SPINN-NP with the added tracking LSTM reaches state-of-the-art accuracy among sentence encoding based models. The success of the SPINN-NP model, which is a hybrid tree-sequence model, suggests that the tree- and sequence-based encoding methods are complementary.

The full SPINN model with its relatively weak internal parser performs more poorly, but nonetheless exceeds the performance of the LSTM baseline. None of our models reached the performance of the strongest attention-based models, which were explicitly engineered for the sentence pair-based structure of the SNLI task.

@@

\begin{figure}
\resizebox{\linewidth}{!}{
\begin{tikzpicture}
\begin{axis}[xmin=0, ymin=0, xlabel=Batch size, ylabel=Feedforward time (sec),
			 xtick={0,256,512,1024,2048}, legend style={at={(1.1, 0.98)},anchor=north east}]
  \addplot table [x={Batch size}, y=CPU, col sep=tab] {runtime.csv};
  \addlegendentry{CPU \cite{irsoy2014deep}}
  \addplot table [x={Batch size}, y=GPU, col sep=tab] {runtime.csv};
  \addlegendentry{Thin-stack GPU}
\end{axis}
\end{tikzpicture}
}
\caption{Runtime performance results with the thin-stack GPU algorithm for tree-structured neural networks. \todo{[JG] Add some comments}}
\end{figure}
